% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{verbatim}
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{Bennet Huber\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{739 S 20th St, Suite 2\\Philadelphia, PA 19146}
\address{bennet.huber@gmail.com\\(215) 490-4297}
                                  
\begin{resume}

\section{Job Objective}
    To work as a backend software developer specializing in algorithm development, optimization,
    and parallel/distributed computing.
 
\section{Education}
    The Pennsylvania State University - May 2010\\
    Bachelors of Science in Computer Science with a minor in Mathematics\\
    GPA 3.55\\
    Dean's list 7/8 semesters

\section{Elective Courses}
   \begin{ncolumn}{2}
       Intro to Cryptography (graduate level) &Intro to Computer Security\\
       Communication Networks &Intro to Computer Architecture\\
       Intro to Abstract Algebra &Intro to Numerical Computations
   \end{ncolumn}
 
\section{Experience}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Software Developer} \>Azavea Inc     \>December 2010 - April 2014\\
                             \>Philadelphia, PA
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   Azavea is a medium sized consulting firm specializing in web/mobile
   applications related to GIS problems.  As a software developer I worked
   on teams of two to six people and projects lasting between a
   few months to many years.  I was a full-stack developer working on
   things such as UI design and implementation, application logic, spatial
   predictive modelling, distributed architecture design, application
   deployment, and database schema design.  One of the primary projects I
   worked on is called HunchLab, a product designed for crime analysts that
   implements many cutting edge crime prediction algorithms and statistical
   models.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Grader for Intro to Computational Theory} \> Penn State Computer Science Department\> Spring 2010\\
                          \>State College, PA
   \end{tabbing}\vspace{-20pt}
    Responsibilities included grading weekly homework assignments for a
    class of 60 (approximately 10 hours/week).
    The course was considered one of the hardest requirements for the CS program.
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Intern}  \> Cisco Systems\> Summers 2007 and 2008\\
                          \>San Jose, CA
   \end{tabbing}\vspace{-20pt}
   Internal web development and administration.


\section{Relevant Skills}
Proficient in C\#/.NET framework, Python, JavaScript, C/C++, Django Framework,
Git/Github, Jenkins CI server administration, SQL (PostGreSQL and MSSQL),
and common Windows/Linux administration tasks.\\
Familiar with Scala, Java, Objective-C/iOS programming, Perl, Scheme, Bash, HTML, CSS,
web visualization, JQuery, Dojo, Angular-JS, Leaflet, GIS, Spatial Analysis,
Virtualbox, Vagrant, Ansible, AWS, Nginx, Subversion, TravisCI,
and many other less relevant technologies.
 
 
\section{Activities and Awards}          
    Recipient of the Lockheed Martin Engineering Scholars Award\\
    Penn State Judo Club\\
    E-House Academic Committee (local student government in college)\\
    Member of the International Thespian Society\\
    Occasional instructor for Girl Develop It Philly\\
    Bicycled across America, Summer 2009

\section{References}
    Available upon request
 
\end{resume}
\end{document}
